Automated Synthesis of State-Space Digital Controllers

### 2016-11-21 cav2017/cav2017.tex
review section LTI representations of ARMA models

Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i]$$
where $y$ is the output of the system and $u$ its input.
The equivalent LTI dynamics of such a model are:
\begin{align}
\vec{x}_k=&\vec{A}\vec{x}_{k-1}+\vec{B}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
y_k=&\vec{C}\vec{x}_k + b_0u_k\nonumber\\
\vec{A}=&\left[
\begin{array}{ccccc}
0&1&0&\cdots&0\\
0&0&1&\cdots&0\\
\vdots&\vdots&\vdots&\ddots&\vdots\\
0&0&0&\cdots&1\\
-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
\end{array}\right],
\vec{B}=\left[
\begin{array}{c}
0\\0\\ \vdots\\ 0\\ 1
\end{array}\right]\nonumber\\
\vec{C}=&[b_n-a_nb_0\ b_{n-1}-a_{n-1}b_0 \cdots b_1-a_1b_0] : b_{i \in (m\ n]}=0\nonumber
\end{align}

>>>>

Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
where $y$ is the output of the system and $u$ its input.
The equivalent LTI dynamics of such a model are:
\begin{align}
\vec{x}_k=&\vec{A}\vec{x}_{k-1}+\vec{B}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
y_k=&\vec{C}\vec{x}_k + b_0u_k\nonumber\\
\vec{A}=&\left[
\begin{array}{ccccc}
0&1&0&\cdots&0\\
0&0&1&\cdots&0\\
\vdots&\vdots&\vdots&\ddots&\vdots\\
0&0&0&\cdots&1\\
-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
\end{array}\right],
\vec{B}=\left[
\begin{array}{c}
0\\0\\ \vdots\\ 0\\ 1
\end{array}\right]\nonumber\\
\vec{C}=&[b_n-a_nb_0\ b_{n-1}-a_{n-1}b_0 \cdots b_1-a_1b_0] : b_{i \in (m\ n]}=0\nonumber
\end{align}
